\subsubsection{Obtaining GeoServer and Aggregate Extension}

GeoServer\footnote{GeoServer: \url{http://www.geoserver.org}} is used to
visually display collected data pre-aggregated with the pre-aggregate
index. An extension has been written for
GeoServer which needs to be included in the web application. This is done
by including the JAR files of the extension in the \lstinline|WEB-INF| of
the GeoServer WAR file. A step by step guide is given below in
\Fref{sec:InstallExtension}. However before following these instructions
the necessary JAR and WAR files need to be obtained.

The GeoServer WAR file can be downloaded from the
\href{http://www.geoserver.org/download/}{\textsf{GeoServer website}}. The
custom Java extension files should be built using the source code. The
extension consists of the \lstinline|pre-aggregate| and
\lstinline|geoserver-ext| projects in the \lstinline|neogeo| project. Note
that first the JAR file of \lstinline|pre-aggregate| should be created as
it is a dependency of \lstinline|geoserver-ext|. The JARs can be built
using the command line or in an IDE such as Eclipse or Netbeans: using the
\lstinline|clean and build| command on a project in Netbeans should build
\lstinline|<project-name>-0.0.1-SNAPSHOT.jar| which can be found in the
\lstinline|target| directory of the respective project.

\subsubsection{Installing Extension}
\label{sec:InstallExtension}

The following instructions assume the geoserver extention files are located
in the directory \lstinline|/data/upload/| and the
\lstinline|geoserver.war| file is located in the directory
\mbox{\lstinline|/data/tmp/tmp_war|}. If this is not the case, the file
paths in the instructions below should be changed accordingly.

\noindent \textit{Unpack the WAR file}
\begin{enumerate}
	\item \lstinline|jar -xvf geoserver.war|
\end{enumerate}
\textit{Copy the JAR files of the extension into \lstinline|WEB-INF/lib| directory of the GeoServer unpacked WAR file}
\begin{enumerate}[noitemsep,resume]
	\item \lstinline|cp /data/upload/pre-aggregate-0.0.1-SNAPSHOT.jar /data/tmp/tmp_war/WEB-INF/lib|
	\item \lstinline|cp /data/upload/geoserver-ext-0.0.1-SNAPSHOT.jar /data/tmp/tmp_war/WEB-INF/lib|
\end{enumerate}
\textit{Recreate the GeoServer WAR file}
\begin{enumerate}[noitemsep,resume]
	\item \lstinline|jar -cvf geoserver.war META-INF/ WEB-INF/ index.html data/|
\end{enumerate}
The GeoServer WAR with the stairwalker extension should now be ready for
deployment.

\subsubsection{Deploying GeoServer}
\label{sec:geotomcat}

After the GeoServer WAR file has been repacked with the aggregate extension
included, it is ready to be deployed in a web server. \Fref{sec:tomcat}
describes how to set up a Tomcat web server. Once the server is
running, it can be accessed locally with
\href{http://localhost:8080/}{\lstinline|http://localhost:8080/|} assuming
default installation configuration were used, otherwise the port number
might be different. In the case that the Tomcat server is installed on a
different machine, the web server can be accessed by replacing
\lstinline|localhost| with the name or IP address of that machine.

From the Tomcat homepage, it should be possible to access the Tomcat manager
webapp. With the default setup it should be possible to login with the
following credentials:\\
\indent \textbf{username:} manager \\
\indent \textbf{password:} tcmanager \\

In the Tomcat manager webapp under the \lstinline|deploy| section, it is
possible to upload a WAR file to be deployed. Select the repacked WAR file
from \Fref{sec:InstallExtension} and deploy the application. Once the
application is deployed it will be displayed in the \lstinline|application|
section of the Tomcat manager webapp. From there, it is possible to follow
the path given for the GeoServer application or, if the default
configuration was used to go to
\mbox{\lstinline|http://<Tomcat-IPaddress>:8080/geoserver/web/|}.
