This section discusses most of the possibilities that GeoServer has to
offer when it comes to the visualization of the data. The GeoServer manual
has some information on this subject, which can be found on:
\url{http://docs.geoserver.org/2.5.x/en/user/styling/sld-reference/index.html}.

In the following, more information on what the differences are between the
certain options and some ways to implement these options. This section uses
some of the examples used in our demo to give some more insight what can be
done and hopefully making it easier to realize what is desired. Most
information can be found on the website, below a discussion is given on
what types are best used when, but also some more information on how to
make them work properly.

\subsubsection{Symbolizers}

In SLD, there are three different symbolizers, a linesymbolizer, a
pointsymbolizer and a polygonsymbolizer. A pointsymbolizer is used when the
data that has to be represented is best shown as points. It does exactly
what it says, you'll get a map with points on it and each point will
represent a data-object from your dataset. This symbolizer can be really
handy in certain situations. For example when you want to show all
locations where a rare species of a bird has been found, it will show a map
with all points where a bird has been reported.

A linesymbolizer is used when the data that has to be displayed is best
shown in lines. This symbolizer is best used to display roads for example.
It isn't a symbolizer that can be used to represent data very well, but it
is more used for pre-defined data, such as rivers, roads etc.

A polygonsymbolizer is used when the data that you want to represent has to
be displayed in two-dimensional objects. There are many possibilities in a
polygonsymbolizer. It is possible to make a simple square but it also has
the option to make circles or triangles. It is one of the most commonly
used symbolizers.  A good example where a polygonsymbolizer is used, is to
display the amount of people living in cities. This can be done with a
circle polygon and that the circle will get bigger when more people live in
a city.

\subsubsection{Filters}

Filters are the most important function when it comes to making a custom
style. A filter is basically the basis of a fancy layer. What a filter does
is that it makes a ruling and if that ruling is met, the color, labeling
etc will be done. In SLD, it is possible to have an unlimited amount of
filters so the possibilities are many. The following filter expression
can be used:

\begin{itemize}
	\item \lstinline|$<$PropertyIsEqualTo$>$|
	\item \lstinline|$<$PropertyIsNotEqualTo$>$|
	\item \lstinline|$<$PropertyIsLessThan$>$|
	\item \lstinline|$<$PropertyIsLessThanOrEqualTo$>$|
	\item \lstinline|$<$PropertyIsGreaterThan$>$|
	\item \lstinline|$<$PropertyIsGreaterThanOrEqualTo$>$|
\end{itemize}
An example on how a single filter can be used is the following:
\begin{lstlisting}
<ogc:Filter>
  <ogc:PropertyIsLessThan>
    <ogc:PropertyName>testvalue</ogc:PropertyName>
    <ogc:Literal>200</ogc:Literal>
  </ogc:PropertyIsLessThan>
</ogc:Filter>
\end{lstlisting}

This example tests if \lstinline|testvalue| is less than \lstinline|200|.
If this is the case, one can specify what the filter should do. Below is
the complete example that does something with this filters.

\begin{lstlisting}
<Rule>
  <Name>SmallPop</Name>
  <Title>Less Than 100</Title>
  <ogc:Filter>
    <ogc:PropertyIsLessThan>
      <ogc:PropertyName>testvalue</ogc:PropertyName>
      <ogc:Literal>100</ogc:Literal>
    </ogc:PropertyIsLessThan>
  </ogc:Filter>
  <PolygonSymbolizer>
    <Fill>
      <CssParameter name="fill">#38FF19
      </CssParameter>
      <CssParameter name="fill-opacity">1.0
      </CssParameter>
    </Fill>
    <Stroke>
      <CssParameter name="stroke">#000000
      </CssParameter>
      <CssParameter name="stroke-width">1.0
      </CssParameter>
    </Stroke>
  </PolygonSymbolizer>
</Rule>
\end{lstlisting}

What this example does is that if the \lstinline|testvalue| is below
\lstinline|100|, it will fill a polygon with the color:
\lstinline|#38FF19|. If this is not the case, it will go to the next rule
(if there is one; otherwise it does nothing). The image shows a graph of
the implementation we made for our data. The image has different kind of
colors for the amount of data in a tile. If the amount is high, the color
will become more red, and if there is little data, the tile will be green.

\subsubsection{Additional Options}

GeoGerver SLD has a lot of options when it comes to customizing the data
display that you've made. Below are some of the important features that are
commonly used in GeoServer.

\textbf{Halo:} A halo gives a glow behind the current label. It should
always be used in a textsymbolizer, since this is the only place where you
can add a halo. To use a halo is very simple: you include
\lstinline|<Halo></Halo>| and in between it is possible to add
\lstinline|<Radius>| and \lstinline|<Fill>|. For more information on how to
use a \lstinline|<Fill>| we refer to the GeoServer SLD cookbook.

\textbf{Anchorpoint:} An anchor point is a handy tool to place your label
in a possible position. It is used as shown below. Important to note is
that you can set where the anchor point is (for example, above the point)
and that you can move it based on the anchor point, for instance make it go
all the way to left (negative X placement) or all the way to the right
(positive X placement)
\begin{lstlisting}
<PointPlacement>
  <AnchorPoint>
    <AnchorPointX>0.5</AnchorPointX>
    <AnchorPointY>0.0</AnchorPointY>
  </AnchorPoint>
  <Displacement>
    <DisplacementX>0</DisplacementX>
    <DisplacementY>25</DisplacementY>
  </Displacement>
  <Rotation>-45</Rotation>
</PointPlacement>
\end{lstlisting}

\textbf{Opacity:} Opacity is the transparency of either a label, point,
polygon or line. It can be used to paint layers over each other (setting
Opacity to 0). It is often used in cases where multiple data sets have to be
displayed in the same tile (used in our example as well). The way you use
it is the following:
\begin{lstlisting}
<Opacity>0.3</Opacity>
\end{lstlisting}

\textbf{Rotation:} Rotation is the function that is used to turn shapes and
labels in SLD. It is handy if you want to turn tiles or make labels line up
with lines better. The way to use it is simply in the section that has to
be rotated just add the following code:
\lstinline|<Rotation>-45</Rotation>| for a negative 45 degree turn.

\textbf{Graphic Fill:} A graphic fill is used in case a picture/image has
to be shown in a layer. It has a lot of possibilities since every
picture/image can be added in this way. The implementation is a little
more complex; below is an example of a graphic fill. 
\begin{lstlisting}
<FeatureTypeStyle>
  <Rule>
    <PolygonSymbolizer>
      <Fill>
        <GraphicFill>
          <Graphic>
            <ExternalGraphic>
              <OnlineResource
              xlink:type="simple"
              xlink:href="colorblocks.png" />
              <Format>image/png</Format>
            </ExternalGraphic>
            <Size>93</Size>
          </Graphic>
        </GraphicFill>
      </Fill>
    </PolygonSymbolizer>
  </Rule>
</FeatureTypeStyle>
\end{lstlisting}
More options and information can be found in the SLD cookbook on the
GeoServer website. This section was meant to give some more insight about 
commonly used functions.
  
